%-------------------------
% Resume in Latex
% Author : Nikunj Rajesh Thakur
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    {\Huge \scshape Nikunj Thakur} \\ \vspace{1pt}
    250 Richvale Drive South, Brampton, ON L6Z4W2 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 647-702-3253 ~ \href{mailto:nrthakurr@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{nrthakurr@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/nrthakur/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/nrthakur}}  ~
    \href{https://github.com/nrthakur}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/nrthakur}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {York University}{Sep. 2021 -- April 2025}
      {Bachelors of Engineering., Spec. Hons. - Software Engineering}{Toronto, ON}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Computer Organization
                \item Advanced OOP
                \item Embedded Systems
                \item Software Development
                \item Operating Systems
                \item Systems Programming
                \item Computer Architecture
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Vin Engineering, inc.}{January 2022 -- April 2022}
      {Software Engineer Intern}{Mississauga, ON}
      \resumeItemListStart
        \resumeItem{Employed Jira to solve over 70 bugs in the Vin Engineering platform and improve cross-browser compatibility}
        \resumeItem{Collaborated with senior developers using Agile framework to facilitate the production of data mining software}
        \resumeItem{Orchestrated company meetings for Vin Engineering’s codebase architecture and programmatic practices}
        \resumeItem{Explored ways to visualize and send a daily report of test results to team members  using HTML, Javascript, and CSS.}
      \resumeItemListEnd

    \resumeSubheading
      {NKM, Inc}{July 2021 -- September 2021}
      {Front End Developer Intern}{Brampton, ON}
      \resumeItemListStart
        \resumeItem{Assisted in development of the front end of a mobile application for iOS/Android using Dart and the Flutter framework.}
        \resumeItem{Worked with Google Firebase to manage user inputted data across multiple platforms including web and mobile apps.}
        \resumeItem{Collaborated with team members using version control systems such as Git to organize modifications and assign tasks.}
        \resumeItem{Utilized Android Studio as a development environment in order to visualize the application in both iOS and Android.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{MessageMe - iOS App} $|$ \emph{Swift, Google Firebase Firestore, Xcode}}{December 2022}
          \resumeItemListStart
            \resumeItem{Produced a messaging application containing full functionality of sending and receiving messages.}
            \resumeItem{Implemented Firebase Firestore database to take advantage of a client first SDK and real-time updates allowing to receive and send messages with ease.}
            \resumeItem{Utilized fundamental UI/UX fundamentals to create an aesthetically appealing design. }
            \resumeItem{Executed prominent message application principals to include: profile picture and timestamps.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{TriviaToday - iOS App} $|$ \emph{Swift, Xcode}}{November 2022}
          \resumeItemListStart
            \resumeItem{Used Swift to build a flawless iOS app that displays Multiple Choice questions to test General Knowledge.}
            \resumeItem{Implemented an API function to pull and generate random questions at every run.}
            \resumeItem{Learned and executed fundamental principles of UI/UX to include animation, progress bar, and instant
depiction of right or wrong answer.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{2048 - Web Game} $|$ \emph{HTML, CSS, JavaScript, VScode}}{October 2022}
          \resumeItemListStart
            \resumeItem{Recreated the 2048 game using experimental methodologies, and taking initiative to execute new concepts
and algorithms.}
            \resumeItem{Utilized fundamental object oriented programming concepts such as setters, getters and encapsulation}
            \resumeItem{Implemented complex logic, CSS animations in JavaScript and classes to increase efficiency and develop a
professional program.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C, HTML/CSS, JavaScript, SQL, PowerShell, PHP, Swift} \\
     \textbf{Developer Tools}{: VS Code, Eclipse, Google Cloud Platform, Android Studio, Xcode} \\
     \textbf{Technologies/Frameworks}{: Linux, Jenkins, GitHub, JUnit, WordPress, Dart, Flutter} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Faculty of Engineering Science}{September 2022 -- Present}{Director of Finance}{York University}
            \resumeItemListStart
                \resumeItem{Collaborated with Vice-President Finance to ensure all financial matters of the Faculty of Engineering Science were being accurately maintained.}
                \resumeItem{ Actively participated in executive board discussions alongside a team of 20 members and attended weekly meetings to oversee progress in essential parts of the faculty.}
                \resumeItem{Led chapter of 30+ members to work towards goals that improve and promote community service, academics, and unity.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
